NIRCam Flux Calibration Plan

### 2017-03-26 ms.tex
I described how NGC 2506 has worse resolution because of the 600 gpm grating. Also, I updated the NGC 2420 classified stars plots to include F9-V and G2 IV-V classification.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
\includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{figNCFOV} after a second Hectospec fiber configuration.
{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
\includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{fig:NCFOV} after a second Hectospec fiber configuration.
{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
\end{figure}

During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
This
